### 2022-11-09 NSF2022/Description/specificaim2.tex
worked on SA2

\begin{wrapfigure}[28]{l}{1.8in}
  \vspace{-8pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} \footnotesize (a) A double well potential. (b)
  The solution of the one-dimensional phase
  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
  Newton's methods.}
\end{wrapfigure}
The PIs have developed numerical methods to solve~\eqref{eqn:phase} when
$W(\phi) = \phi^2$---this choice results in the linear screened Laplace
equation. For a general double well potential $W$ with local minima at
$\phi_0$ and $\phi_1$, we propose to interpret the solution as the root
finding problem for
\begin{align}
  \label{eqn:phaseRoot}
  J[\phi] = -\epsilon^2 \Delta \phi + \tfrac{1}{2}W'(\phi).
\end{align}
Equation~\eqref{eqn:phaseRoot} will be solved with Newton's method,
$\phi^{N+1} = \phi^{N} - \alpha (dJ^N)^{-1} J(\phi^N)$, where $dJ^N =
-\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the Fr\'{e}chet
derivative of $F$, and $\alpha$ is the step size that will be determined
using backtracking. This requires Solving the variable coefficient PDE
$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = J[\phi^N]$ with an
integral equation, but this is challenging since a fundamental solution
is not readily available. However, by choosing a double well potential
with $W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
inexact Newton's method where $dJ^{-1}$ is approximated by solving
$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We test the
efficacy of the exact and inexact Newton's method applied
to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dJ$
with a second-order finite difference stencil. The double well potential
is illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
Newton's methods converge to the solution in Figure~\ref{fig:CA}(b).
Figure~\ref{fig:CA}(c) shows the norm of the residual at each Newton
iterate when using the exact second derivative (red curve) and the
approximate second derivative (blue curve). While the inexact Newton's
method requires roughly twice as many iterations to reach of a tolerance
of $10^{-4}$, each iteration is significantly cheaper to apply.

Having demonstrated that the inexact Newton method converges in one
dimension, it will be coupled with IE formulations to
solve~\eqref{eqn:phase} in two and three dimensions. The solution of
$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$ can be written
as $v = v^P + v^H$ where $v^P$ is a volume potential and
$v^H$ is the double layer potential. The volume potential is
\begin{align*}
  v^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) J[\phi^N](\yy)\, d\yy, 
    \quad \xx \in \Omega(t),
\end{align*}
where $G$ is the fundamental solution of $-\epsilon^2 \Delta +
\tfrac{\beta}{2}$. Volume potentials are more challenging to numerically
compute than layer potentials, but methods have recently been developed
to accurately and efficiently compute volume
potentials~\cite{fry-leh-tor2018, and-zhu-vee2022}. The boundary
condition will be enforced using $\phi^H(\xx)$ which will be represented
as a double-layer potential. This approach of combining volume and layer
potentials has successfully been used by PI BQ~\cite{kro-qua2010} and
others~\cite{fry-kro-tor2019, kli-ask-kro2020, che-hua-lei2005}.

>>>>

\begin{wrapfigure}[28]{l}{1.8in}
  \vspace{-8pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} \footnotesize (a) A double well potential. (b)
  The solution of the one-dimensional phase
  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
  Newton's methods.}
\end{wrapfigure}
The PIs have developed numerical methods to solve~\eqref{eqn:phase} when
$W(\phi) = \phi^2$---this choice results in the linear screened Laplace
equation. For a general double well potential $W$ with local minima at
$\phi_0$ and $\phi_1$, we propose to interpret the solution as the root
finding problem for
\begin{align}
  \label{eqn:phaseRoot}
  J[\phi] = -\epsilon^2 \Delta \phi + \tfrac{1}{2}W'(\phi).
\end{align}
Equation~\eqref{eqn:phaseRoot} will be solved with Newton's method,
$\phi^{N+1} = \phi^{N} - \alpha (dJ^N)^{-1} J(\phi^N)$, where $dJ^N =
-\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the Fr\'{e}chet
derivative of $F$, and $\alpha$ is the step size that will be determined
using backtracking. This requires solving the variable coefficient PDE
$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = J[\phi^N]$, which
is challenging with an integral equation since a fundamental solution is
not readily available. However, by choosing a double well potential with
$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
inexact Newton's method where $dJ^{-1}$ is approximated with the
solution of $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We
test the efficacy of the exact and inexact Newton's method applied
to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dJ$
with a second-order finite difference stencil. The double well potential
is illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
Newton's methods converge to the solution in Figure~\ref{fig:CA}(b).
Figure~\ref{fig:CA}(c) shows the norm of the residual at each Newton
iterate when using the exact second derivative (red curve) and the
approximate second derivative (blue curve). While the inexact Newton's
method requires roughly twice as many iterations to reach of a tolerance
of $10^{-4}$, each iteration is significantly cheaper to apply.

Having demonstrated that the inexact Newton method converges in one
dimension, it will be coupled with IE formulations to
solve~\eqref{eqn:phase} in two and three dimensions. The solution of
$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$ can be written
as $v = v^P + v^H$ where $v^P$ is a volume potential and $v^H$ is a
homogeneous solution of the PDE, which is represented as a layer
potential, and is used to satisfy the boundary condition. The volume
potential is
\begin{align*}
  v^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) J[\phi^N](\yy)\, d\yy, 
    \quad \xx \in \Omega(t),
\end{align*}
where $G$ is the fundamental solution of $-\epsilon^2 \Delta +
\tfrac{\beta}{2}$. Traditionally, volume potentials are more challenging
to compute than layer potentials, but new methods have recently been
developed that allows them to be computed accurately and
efficiently~\cite{fry-leh-tor2018, and-zhu-vee2022}. This approach of
combining volume and layer potentials has successfully been used by PI
BQ~\cite{kro-qua2010} and others~\cite{fry-kro-tor2019, kli-ask-kro2020,
che-hua-lei2005}.
